\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2016-07-19 minimal.tex
Version 1.2.6

@@

>>>>

\jsonDirectory{examples/json}
\jsonFile{examples/json/nested/cake.json}{cake}

@@

The following Chart uses information from JSON-files. \\[3pt]
\chart[width=0.45\textwidth, height=0.3\textwidth, logscale=true, chartType=line]{SELECT a, b, c FROM json_files WHERE json_filename LIKE 'run\%';}
\chart[width=0.45\textwidth, height=0.3\textwidth, logscale=true, chartType=line, name=testname]{SELECT a, b, c FROM json_files WHERE c > 5 AND json_filename LIKE 'run\%';} \\[3pt]

To check if the results from JSON-files contain correct data, one can insert his own data for comparision. Examples to drag and drop can be found in the examples folder.
\begin{itemize}
\item This JSON has correct values \json{run1}
\item Here some values are changed \json{run4}
\item And here are many nested values \json{cake}
\end{itemize}

### 2016-07-19 pdbf-doc.tex
Version 1.2.6

\title{\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
}
\date{}

@@

@@

\section{Thanks to}
phantomJS (\url{https://github.com/ariya/phantomjs})\\
Apache Commons (\url{http://commons.apache.org/})\\
Apache PDFBox (\url{https://pdfbox.apache.org/})\\
jTar (\url{https://github.com/kamranzafar/jtar})\\
google-gson (\url{https://github.com/google/gson})\\
postgreSQL JDBC Driver (\url{https://jdbc.postgresql.org/})\\
MariaDB JDBC Driver (\url{https://mariadb.com/kb/en/mariadb/about-the-mariadb-java-client/})\\
AlaSQL (\url{https://github.com/agershun/alasql})\\
C3 (\url{https://github.com/masayuki0812/c3})\\
D3 (\url{https://github.com/mbostock/d3})\\
Codemirror (\url{https://github.com/codemirror/codemirror})\\
google-diff-match-patch (\url{https://code.google.com/p/google-diff-match-patch/})\\
explorercanvas (\url{https://code.google.com/p/explorercanvas/})\\
DataTables (\url{https://github.com/DataTables/DataTables})\\
jQuery (\url{https://github.com/jquery/jquery})\\
jQuery-UI (\url{https://github.com/jquery/jquery-ui})\\
jStat (\url{https://github.com/jstat/jstat})\\
pivottable (\url{https://github.com/nicolaskruchten/pivottable})\\
PDF.js (\url{https://github.com/mozilla/pdf.js})\\
google-closure-compiler (\url{https://github.com/google/closure-compiler})\\
lz-string (\url{https://github.com/pieroxy/lz-string})\\
YUI Compressor (\url{https://github.com/yui/yuicompressor})\\

@@

\subsection{SQL}
\noindent Macros: \\[3pt]
\verb|\dbSQLText{sqlQueryString}| \\
\verb|\dbSQLFile{fileWithSQLQueries}| \\
\textbf{Note:} Relative filepaths are relative to the tex file.\\
\verb|\dbSQLJDBC{jdbcConnectionURL}{user}{password}{commaSeperatedListOfTableNames}| \\
\textbf{Note:} jdbcConnectionURL consist of jdbc followed by the name of the dbms (only postgresql and mysql are currently supported) followed by the url of the dbms followed by the database name (e.g. jdbc:postgresql://localhost:5432/postgres).\\
\textbf{Note:} jdbcConnectionURL, user, and password are not stored in the output documents.\\[4pt]

@@

>>>>

\title{\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation}
\author{
 Patrick Bender \hspace{2cm} Lukas Lange \hspace{2cm} Shoaib Malik\\
  \texttt{\{s9pabend, s9lslang, s9mumali\}@stud.uni-saarland.de}
}
\date{}

@@

\subsection{Enable the comparison of your results to other users}
To make your own results even more transparent, you can let other users input their own result files. If there is a difference, the PDBF will recognize it, and will automaticly create a highlighted view of changes. However right now, this option is only avaible for JSON-files as datasource.

@@

\section{Thanks to}
phantomJS (\url{https://github.com/ariya/phantomjs})\\
Apache Commons (\url{http://commons.apache.org/})\\
Apache PDFBox (\url{https://pdfbox.apache.org/})\\
jTar (\url{https://github.com/kamranzafar/jtar})\\
google-gson (\url{https://github.com/google/gson})\\
postgreSQL JDBC Driver (\url{https://jdbc.postgresql.org/})\\
MariaDB JDBC Driver (\url{https://mariadb.com/kb/en/mariadb/about-the-mariadb-java-client/})\\
AlaSQL (\url{https://github.com/agershun/alasql})\\
C3 (\url{https://github.com/masayuki0812/c3})\\
D3 (\url{https://github.com/mbostock/d3})\\
Codemirror (\url{https://github.com/codemirror/codemirror})\\
google-diff-match-patch (\url{https://code.google.com/p/google-diff-match-patch/})\\
jsondiffpatch (\url{https://github.com/benjamine/jsondiffpatch}) \\
explorercanvas (\url{https://code.google.com/p/explorercanvas/})\\
DataTables (\url{https://github.com/DataTables/DataTables})\\
jQuery (\url{https://github.com/jquery/jquery})\\
jQuery-UI (\url{https://github.com/jquery/jquery-ui})\\
jStat (\url{https://github.com/jstat/jstat})\\
pivottable (\url{https://github.com/nicolaskruchten/pivottable})\\
PDF.js (\url{https://github.com/mozilla/pdf.js})\\
google-closure-compiler (\url{https://github.com/google/closure-compiler})\\
lz-string (\url{https://github.com/pieroxy/lz-string})\\
YUI Compressor (\url{https://github.com/yui/yuicompressor})\\

@@

\subsection{SQL}
\noindent Macros: \\[3pt]
\verb|\jsonFile{path/to/file}{filename} | \\
\verb|\jsonDirectory{path/to/directory}| \\
\textbf{Note:} Relative filepaths are relative to the tex file.\\
\verb|\dbSQLJDBC{jdbcConnectionURL}{user}{password}{commaSeperatedListOfTableNames}| \\
\textbf{Note:} jdbcConnectionURL consist of jdbc followed by the name of the dbms (only postgresql and mysql are currently supported) followed by the url of the dbms followed by the database name (e.g. jdbc:postgresql://localhost:5432/postgres).\\
\textbf{Note:} jdbcConnectionURL, user, and password are not stored in the output documents.\\[4pt]

\subsection{JSON}
\noindent Macros: \\[3pt]
\verb|\dbSQLText{sqlQueryString}| \\
\verb|\dbSQLFile{fileWithSQLQueries}| \\
\textbf{Note:} Relative filepaths are relative to the tex file.\\
\textbf{Note:} The \verb|\dbSQLFile{fileWithSQLQueries}|-command will search the whole directory (it will not scan deeper file structures), and chooses the filename according to existing filename. \\
\textbf{Note:} You can insert as many JSON-commands as you like. \\[3pt]

@@

\noindent\textbf{Note:} To choose JSON-files as your datasource for charts, add to your SQL-FROM clause \texttt{json-files} and to your SQL-WHERE clause \texttt{filename LIKE \%What You Want\%) \\[3pt]
